---
title: "Why youshoulduse QuartoPresentation"
author:
  name: "SenS"
  email: an.santoni22@gmail.com
format: 
  revealjs:
    theme: [dark, custom.scss]
    self-contained: true
    scrollable: true
    footer: "bCOOL use4to"
    incremental: true
    slide-number: c/t
    show-slide-number: all
editor: visual

---

```{r}
#| include: false

library(tidyverse)
library(ggplot2)
```


# Y use Quarto presentation

## Advantages

* It's cool
* It's interactive
* Everyone is going to be astonished

## Disadvantages

* HTML presentation are not stable
* You will not be invited at conferences

## FIRST THINGS FIRST

* GET YOUR YAML RIGHT
* set your revealjs with self-contained: true
* if you want to have incremental content, go for incremental: true, you can adjust non incremental stuff later.
* otherwise you can specify incremental: false and you can force increments later using . . .  (3 columns)
* then you may setup email, footer, logo, show-slide-number 

## How do i put content in different lines

I can either use <.br> <br>

or I put 2 spaces at the end of the line  
let's try

## customize your theme

put theme: [dark, custom.scss] in your YUUUUMMML to modify the theme you want until you make it perfect.


##

```{r}
#| fig-align: center
#| code-line-numbers: "|2|3|"

mtcars %>%                               
  ggplot( aes(mpg, hp)) +   
  geom_point() 

```


## {auto-animate="true"}

```{r}

mtcars %>%                               
  ggplot( aes(mpg, hp, color = gear)) +   
  geom_point() + 
  geom_smooth(method = "lm")
```

##
